---
title: "Airbnb New User Bookings"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}

#### Load Packages ----
packages <- c(
  "data.table", # Data Manipulation
  "bit64",      # To load datatype integer64 
  "plotly",     # Visualisations
  "GGally",     # Visualisations - heat map
  "dplyr",      # Data Manipulation
  "ggplot2",    # Visualisations
  "wordcloud",  # Visualisations
  "scales",
  "forcats",
  "e1071",      # skewness function
  "rmarkdown",  # rmarkdown::render
  "caret"       # Modelling
)

load_packages <- function(packages){
  new.packages <- packages[!(packages %in% installed.packages()[, "Package"])]
  if (length(new.packages)){
    install.packages(new.packages)
  } 
  sapply(packages, require, character.only = TRUE)
}

load_packages(packages)


```

```{r}

dir.home <- getwd ()

source( "98_parameters.R")

#### functions ----
source( "99_functions.R")

```

```{r etl}

#### etl ---
path_fact.destinations <- file.path(dir.input, "fact.destinations.csv")
path_fact.sessions <- file.path(dir.input, "fact.sessions.csv")
if (!file.exists(path_fact.destinations) | !file.exists(path_fact.sessions)){
  source(file.path(dir.home, "1.1_etl.R"))
}

#### Read in data
fact.destinations <- fread(path_fact.destinations)
fact.sessions <- fread(path_fact.sessions)

fact.destinations[, ":=" (
  date_account_created = convert_date_format(date_account_created),
  date_first_booking = convert_date_format(date_first_booking),
  date_first_active = convert_date_format(date_first_active)
)]

# Remove NDF users
fact.destinations <- fact.destinations[country_destination != ""]
fact.destinations <- fact.destinations[country_destination != "NDF"]

```

```{r eda}


#### eda ----

#### parameters ----
# source(file.path(dir.home, "98_parameters.R"))
dir.data <- file.path(dir.home, "airbnb-recruiting-new-user-bookings")
dir.input <- file.path(dir.home, "input")

#### Markdown captions
library(captioner)
table_captions <- captioner::captioner(prefix = "Tab.")
figure_captions <- captioner::captioner(prefix = "Fig.")

t.ref <- function(label){
  stringr::str_extract(table_captions(label), "[^:]*")
}

f.ref <- function(label){
  stringr::str_extract(figure_captions(label), "[^:]*")
}

```




__FUNCTIONS__
```{r,  eval = TRUE}
#### functions ----
# source(file.path(dir.home, "99_functions.R"))
#### Change Date Format ####
convert_date_format <- function(x){
  as.Date(x, format = "%Y-%m-%d")
}

#### Get mode ####
getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}

# https://stackoverflow.com/questions/22439540/how-to-get-week-numbers-from-dates
find_Weekday_Index <- function(myDate){
  # Find out the start day of week 1; that is the date of first Mon in the year
  myDate <- convert_date_format(myDate)
  weekDay <- weekdays(myDate)
  
  weekDay_index <- 
    ifelse(
      weekDay == "Monday",
      1,
      ifelse(
        weekDay == "Tuesday",
        2,
        ifelse(
          weekDay == "Wednesday",
          3,
          ifelse(
            weekDay == "Thursday",
            4,
            ifelse(
              weekDay == "Friday",
              5,
              ifelse(
                weekDay == "Saturday",
                6,
                ifelse(
                  weekDay == "Sunday",
                  7,
                  0
                )
              )
            )
          )
        )
      )
    )

  return(weekDay_index)
}
```

__ETL__
```{r, eval = TRUE}
#### etl ---
# source(file.path(dir.home, "01_etl.R"))
fact.train <- fread(file.path(dir.data, "train_users_2.csv"))
fact.test <- fread(file.path(dir.data, "test_users.csv"))

# Data type
fact.train[, dataset_type := "TRAIN"]
fact.test[, ":=" (country_destination = NA, dataset_type = "TEST")]


fact.train$date_first_booking<-as.character(fact.train$date_first_booking)
fact.test$date_first_booking<-as.character(fact.test$date_first_booking)

# Combine Train and Test
fact.destinations <- rbind(fact.train, fact.test)

# Extract date_first_active and hour_first_active from timesteamp_first_active
fact.destinations[, year_active := floor(timestamp_first_active / 10000000000)
                  ][, month_active := floor((timestamp_first_active - year_active * 10000000000) / 100000000)
                  ][, day_active := floor((timestamp_first_active - year_active * 10000000000 - month_active * 100000000) / 1000000)
                  ][, hour_first_active := floor((timestamp_first_active - year_active * 10000000000 - month_active * 100000000 - day_active * 1000000) / 10000)
                  ][, date_first_active := as.Date(paste(year_active, month_active, day_active, sep = "-"), format = "%Y-%m-%d")
                  ][, ":=" (year_active = NULL, month_active = NULL, day_active = NULL)]

# Convert date format for date_accounted_created and date_first_booking
fact.destinations <- 
  fact.destinations[, ":=" (
    date_account_created = convert_date_format(date_account_created),
    date_first_booking = convert_date_format(date_first_booking)
  )]
# fact.destinations[, .N, by = .(dataset_type, country_destination, date_first_booking)][is.na(date_first_booking)]

# Build new features - days between active, account, booking
fact.destinations[, ":=" (days_from_active_to_account = date_account_created - date_first_active,
                          days_from_account_to_booking = date_first_booking - date_account_created, # some people book it without an account
                          days_from_active_to_booking = date_first_booking - date_first_active
                          )]

# Adding year, month, year-month features
fact.destinations[, ":=" (
  date_first_booking_end_week = convert_date_format(date_first_booking + 7 - find_Weekday_Index(date_first_booking)),
  first_active_year_month =  format(as.Date(date_first_active), "%Y-%m"),
  first_account_year_month =  format(as.Date(date_account_created), "%Y-%m"),
  first_booking_year_month =  format(as.Date(date_first_booking), "%Y-%m"),
  first_booking_year = year(date_first_booking),
  first_booking_month = month(date_first_booking)
)]
```

__JOIN DIM TABLES TO MAIN TABLE__
```{r, eval = TRUE}
#### Joining to other csv's ####
dim.age_gender <- fread(file.path(dir.data, "age_gender_bkts.csv"))
dim.country <- fread(file.path(dir.data, "countries.csv"))

### 1.0 Join to age_gender_bkts to get population_in_thousands
dim.age_gender[, ":=" (gender2 = ifelse(gender == "male", "MALE", "FEMALE"))][, gender := gender2][, gender2 := NULL]

fact.destinations[, age_bucket_key := floor(age / 5) + 1][, age_bucket_key := ifelse(age_bucket_key >= 21, 21, age_bucket_key)]
age_bucket <- unique(dim.age_gender[, .(age_bucket)])
n_age_bucket <- nrow(age_bucket)
age_bucket <- age_bucket[, age_bucket_key := n_age_bucket - 1:n_age_bucket + 1]
fact.destinations <- 
  merge(
    fact.destinations,
    age_bucket,
    by = "age_bucket_key",
    all.x = TRUE
  )[, age_bucket_key := NULL]

fact.destinations <-
  merge(
    fact.destinations,
    dim.age_gender[, year := NULL],
    by = c("age_bucket", "country_destination", "gender"),
    all.x = TRUE
  )

### 2.0 Join with countries.csv
fact.destinations <-
  merge(
    fact.destinations,
    dim.country,
    by = "country_destination",
    all.x = TRUE
  )

```

__REMOVE NDF__
```{r, eval = TRUE}
# Remove NDF users
fact.destinations <- fact.destinations[country_destination != ""]
fact.destinations <- fact.destinations[country_destination != "NDF"]
```

# Data Visualisation
This section will explore visualisation of various variables in the dataset. For many of these visualisations, we will look particuarly closely at the relationship between our response variable, the country destination, and the various predictors. 

## Response Variable: First Destination Country
First, we explore the response variable; the first destination country. Our classification problem aims to predict the first country that users will book after signing up to the Airbnb site. After removing the NDF category, the response variable consists of 11 categories; 10 countries and the category `Other`. 

```{r fig1, eval = TRUE, fig.cap = figure_captions("fig:fig1", "Number of user bookings per country destination")}
### The Distribution of the Response Variable - Country Destinations
country_destination_dt <- fact.destinations[!(country_destination %in% c("", "NDF") ), .N, by = country_destination][order(-N)]
p <- plot_ly(
  x = country_destination_dt[, country_destination],
  y = country_destination_dt[, N],
  type = "bar") %>% 
  layout(
    title = "Numbers of Booking by Country Destination",
    xaxis = list(
      title = "Country Destinations",
      categoryorder = "array",
      categoryarray = country_destination_dt[, country_destination]
    ),
    yaxis = list(
      title = "Numbers of Booking"
    )
  )
p

```


As discussed earlier, the largest class of first destination is `US`. In fact, after removing NDF observations, the US comprises approximately 70.2% of the remaining observations. As observed in `r f.ref("fig:fig1")`, this class dominates all other classes significantly. Since all users in the dataset originate from the United States, this is a reflection of the fact that the majority of Airbnb travel is for domestic travel - hardly a surprising result. Of the remaining 29.8%, the largest category is `other`, which represents all destinations not individually listed. Finally, the remaining categories include Australia, Canada, and various Western European countries (including France, Italy, Spain, Great Britain, The Netherlands and Portugal). 


# Missing Data Issues
We now explore several variables with notable missing data issues. In particular, we discuss the variable `gender`. 

## Gender
One important consideration for later data cleaning is the breakdown of the `Gender` variable. `r f.ref("fig:fig4")` below shows that 32.6% of the observations report a gender 'unknown'. Importantly, this is different to 'OTHER', which we might suppose belongs to a small proportion of users (<0.2%) who do not identify with either gender. In the case of 'unknown', it seems reasonable that while a small proportion might also belong to the 'OTHER' category, the majority will be users who have chosen not to record a gender upon signup.

In the data cleaning stage, this may cause issues since this we cannot remove 33% of observations, nor would it be reasonable to consider 'Unknown' to be a category of its own. We therefore consider imputing the missing data before further analysis.
```{r fig4, eval = TRUE, fig.cap = figure_captions("fig:fig4", "Proportion of user gender")}
### Gender
gender_summary <- fact.destinations[, .N, by = gender][, proportion := N/sum(N)]
p <- plot_ly(
  data = gender_summary,
  labels = ~gender, 
  values = ~proportion, 
  type = 'pie',
  textposition = 'inside',
  textinfo = 'label+percent',
  insidetextfont = list(color = '#FFFFFF'),
  marker = list(colors = c('rgb(128,133,133)', 'rgb(211,94,96)', 'rgb(114, 147, 203)', 'rgb(144,103,167)'), # unknown, female, male, other
                line = list(color = '#FFFFFF', width = 1)),
  showlegend = TRUE,
  hoverinfo = 'text',
  text = ~paste0("Count: ", N)
) %>%
  layout(
    title = "Proportion of Gender"
  )
p
```

# Interesting Explanatory Variables
## Age:
We explore the variable age as a potentially important predictor of destination. `r f.ref("fig:fig2")` shows the distribution of the age brackets from which users originate. Although Airbnb provides methods of verification online, new users are generally not required to submit proof of age. As such, there are inevitably some age readings which we expect to be false. In particular, we observe in the plot below that there are a disproportionately large number of users (1330 in total) who report ages of over 100, and 5 users who report ages of between 0 and 4 years. Since Airbnb requires users to be at least 18 years old to create an account, we can expect that although some may be in fact over 100 years of age, many of these will be false inputs, or users who have registered illegally. In further data cleaning, we propose to remove all observations who report ages of <18 and >100. 

Moreover, we can observe from `r f.ref("fig:fig2")` that the majority of users are between the ages of 25-30, with the number of users monotonically decreasing from `30-34` until `95-99`. 
```{r fig2, eval = TRUE, fig.cap = figure_captions("fig:fig2", "Number of user bookings by user age group")}
### Age Band
age_bucket_dt <- fact.destinations[!(is.na(age)), .N, by = .(age, age_bucket)
                                   ][order(age)
                                   ][, .(N = sum(N)), by = .(age_bucket)]

age_bucket_dt<- age_bucket_dt %>% mutate(id = seq(1, 20))

ggplot(
  data = age_bucket_dt, 
  aes(x = reorder(age_bucket, id), y = N)
) + 
geom_bar(stat="identity", fill = "plum") +
theme_bw() + 
theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
labs(x = "age group", title = "Age group distribution", y = "Number of bookings")
```

```{r fig3, eval = TRUE, fig.cap = figure_captions("fig:fig3", "Distribution of user ages by country")}
### Age Boxplot
fact.destinations %>%
  filter(age < 110) %>%
  ggplot(.) +
  geom_boxplot(mapping = aes(x = reorder(country_destination, age, FUN = mean), y = age), fill = "plum") +
  coord_flip()+
  labs(x = "country", title = "Age Distribution By Country")+
  theme_bw() + #lot ggplot2 version
  theme(plot.title = element_text(hjust = 0.5))

median <- aggregate(x = fact.destinations$age, by = list(fact.destinations$country_destination), FUN = "median", na.rm = TRUE)
skewness <- aggregate(x = fact.destinations$age, by = list(fact.destinations$country_destination), FUN = "skewness", na.rm = TRUE)
df <- data.frame(Country = median[,1], Median = median[,2], Skewness = skewness[,2] )
df
```
From the boxplot (`r f.ref("fig:fig3")`) and data summary above, we observe that the for all countries, the median of the users age at first booking occurs between 32 and 35. The country with the youngest median age at first booking is Spain (at 32 years), while Great Britain and Australia have the highest median ages at 35. We also observe that all countries return high skewness, indicating a longer upper tail. In particular, we note that Australia has a very high skewness statistic of 20.09 suggesting perhaps, that Australia is more popular amongst older travellers than younger travellers. The positive skewness for all countries is likely due to the asymmetry of user ages, since users are unable to make bookings until they are at least 18 years old but may continue to do so until death.


```{r}
# Extract date_first_active and hour_first_active from timesteamp_first_active
fact.destinations[, year_active := floor(timestamp_first_active / 10000000000)
                  ][, month_active := floor((timestamp_first_active - year_active * 10000000000) / 100000000)
                  ][, day_active := floor((timestamp_first_active - year_active * 10000000000 - month_active * 100000000) / 1000000)
                  ][, hour_first_active := floor((timestamp_first_active - year_active * 10000000000 - month_active * 100000000 - day_active * 1000000) / 10000)
                  ][, date_first_active := as.Date(paste(year_active, month_active, day_active, sep = "-"), format = "%Y-%m-%d")
                  ][, ":=" (year_active = NULL, month_active = NULL, day_active = NULL)]

# Convert date format for date_accounted_created and date_first_booking
fact.destinations <- 
  fact.destinations[, ":=" (
    date_account_created = convert_date_format(date_account_created),
    date_first_booking = convert_date_format(date_first_booking)
  )]
# fact.destinations[, .N, by = .(dataset_type, country_destination, date_first_booking)][is.na(date_first_booking)]

# Build new features - days between active, account, booking
fact.destinations[, ":=" (days_from_active_to_account = date_account_created - date_first_active,
                          days_from_account_to_booking = date_first_booking - date_account_created, # some people book it without an account
                          days_from_active_to_booking = date_first_booking - date_first_active
                          )]

# Adding year, month, year-month features
fact.destinations[, ":=" (
  date_first_booking_end_week = convert_date_format(date_first_booking + 7 - find_Weekday_Index(date_first_booking)),
  first_active_year_month =  format(as.Date(date_first_active), "%Y-%m"),
  first_account_year_month =  format(as.Date(date_account_created), "%Y-%m"),
  first_booking_year_month =  format(as.Date(date_first_booking), "%Y-%m"),
  first_booking_year = year(date_first_booking),
  first_booking_month = month(date_first_booking)
)]
```


# Interesting Explanatory Variables Continued ...
## Date of Bookings
The dataset includes observations from 2009 up to 2015. `r f.ref("fig:fig5")` shows an overall positive trend in the number of data counts over time. The number of user signups, starts low in 2009 (just one year after Airbnb was founded), and increases dramatically throughout the years. There is however, a significant drop in the number of observations after June 2014. This can largely be explained by the fact that the test set requires prediction of data from July 2014. Furthermore, the Kaggle competition initially commenced around July 2014. Later, the competition was re-started in December 2015, and all datasets updated, explaining the presence of a small number of observations in early 2015. 

Strong seasonality effects are also evident, showing peaks around each summer period (mid-year), as well as a significant drop around late December/early January, which is consistent with users either avoiding travel to spend the festive season with family, or staying with family and therefore making fewer bookings through Airbnb. 

```{r fig5, eval = TRUE, fig.cap = figure_captions("fig:fig5", "Number of user bookings per month")}
### First Active / Account Created / First Booking Counts by Year Month
year_month_all <- data.table(
  year_month = sort(unique(c(
    fact.destinations[, first_active_year_month],
    fact.destinations[, first_account_year_month],
    fact.destinations[, first_booking_year_month]
  )))
)[year_month != ""]
 
year_month_full <-
  merge(
    merge(
      merge(
        year_month_all,
        fact.destinations[, .(active.N = .N), by = .(first_active_year_month)],
        by.x = "year_month",
        by.y = "first_active_year_month",
        all.x = TRUE
      ),
      fact.destinations[, .(account.N = .N), by = .(first_account_year_month)],
      by.x = "year_month",
      by.y = "first_account_year_month",
      all.x = TRUE
    ),
    fact.destinations[, .(booking.N = .N), by = .(first_booking_year_month)],
    by.x = "year_month",
    by.y = "first_booking_year_month",
    all.x = TRUE
  )

p <- plot_ly(x = year_month_full[, year_month], 
              y = year_month_full[, active.N], 
              name = 'Active',
              type = 'scatter', 
              mode = 'lines') %>%
  add_trace(y = year_month_full[, account.N], name = 'Account', mode = 'lines') %>%
  add_trace(y = year_month_full[, booking.N], name = 'Booking', mode = 'lines') %>%
  layout(
    title = "Number of bookings by month",
    xaxis = list(title = "Month"),
    yaxis = list(title = 'Booking Counts'), 
    barmode = 'stack'
  )

p
```

`r f.ref("fig:fig6")`below presents a breakdown of the aggregated monthly bookings per destination. This plot shows a the seasonality pattern in greater detail; we are able to observe that while almost all countries display a peak around the 5th-7th month of the year, Australia (`AU`) is the only destination which does not follow this pattern. The bookings for Australia are instead higher in December and January (during the Australian summer), with a dip in the middle of the year and thus follows a pattern of peak/off-season according to the weather seasons. 

__Note:__ due to the size of the class `US`, the inclusion of `US` in `r f.ref("fig:fig6")` somewhat obscures the seasonality patterns for the remaining countries. Using the interactive features of `plotly`, we recommend hiding the `US` line in order to better observe the patterns in other countries, such as Australia. 
```{r fig6, eval = TRUE, fig.cap = figure_captions("fig:fig6", "Number of user bookings per month by country destination")}
### Country Destinations by First Booking Month
destination_by_month <- fact.destinations[, .N, by = .(first_booking_month, country_destination)]
destination_by_month_wide <- dcast(
  destination_by_month,
  first_booking_month ~ country_destination,
  value.var = "N"
)
p <- plot_ly(x = destination_by_month_wide$first_booking_month,
               y = destination_by_month_wide$US,
              type = 'scatter',
              mode = 'lines',
               name = 'US') %>%
  add_trace(y = destination_by_month_wide$other, name = 'OTHER') %>%
  add_trace(y = destination_by_month_wide$FR, name = 'FR') %>%
  add_trace(y = destination_by_month_wide$IT, name = 'IT') %>%
  add_trace(y = destination_by_month_wide$GB, name = 'GB') %>%
  add_trace(y = destination_by_month_wide$ES, name = 'ES') %>%
  add_trace(y = destination_by_month_wide$CA, name = 'CA') %>%
  add_trace(y = destination_by_month_wide$DE, name = 'DE') %>%
  add_trace(y = destination_by_month_wide$NL, name = 'NL') %>%
  add_trace(y = destination_by_month_wide$AU, name = 'AU') %>%
  add_trace(y = destination_by_month_wide$PT, name = 'PT') %>%
  layout(
    title = "Number of bookings each month by country destination",
    xaxis = list(title = "Month"),
    yaxis = list(title = 'Booking Counts')#,
    # barmode = 'stack'
  )
p
```

## User Language Preferences
```{r fig7, eval = TRUE, fig.cap = figure_captions("fig:fig7", "Proportion of non-English language preference in each country destination")}
### Language Preferences by Each Country Destination
fact.destinations %>% 
  filter(language!= "en") %>% 
  group_by(country_destination, language) %>% 
  summarise(n = n()) %>% 
  group_by(country_destination) %>% 
  mutate(nn = n/sum(n)) %>% 
  ggplot(., aes(x = country_destination, y = n)) +
  geom_col(aes(fill=language), width = 0.5, position = "fill") + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6)) + 
  labs(title="Proportion of non-English language preference") +
  theme_classic()
```

```{r fig18, eval = TRUE, fig.cap = figure_captions("fig:fig18", "Proportion of English Speaking Users v.s. Non-English Speaking users")}
### Language Preferences by Each Country Destination
english_summary <- fact.destinations[, .(language_eng = ifelse(language == "en", "English", "Non-English"))
                                     ][, .N, by = language_eng
                                     ][, proportion := N/sum(N)]

p <- plot_ly(
  data = english_summary,
  labels = ~language_eng,
  values = ~proportion,
  type = 'pie',
  textinfo = 'label+percent',
  insidetextfont = list(color = '#FFFFFF'),
  marker = list(colors = c('rgb(114, 147, 203)', 'rgb(211,94,96)'),
                line = list(color = '#FFFFFF', width = 1)),
  showlegend = TRUE,
  hoverinfo = 'text',
  text = ~paste0("Count: ", N)
) %>%
  layout(
    title = "Proportion of English Speaking v.s. Non-English Speaking"
  )
p
```

`r f.ref("fig:fig7")` shows the international language preference (user setting) for non-English accounts against the first booking destination. The pie chart `r f.ref("fig:fig18")` shows the proportion of languages for users overall. We can observe that 97.5% of all users from the dataset have English set as their profile language preference; hardly a surprising result since all users originate from the US. However, it is interesting to note that the non-English proportion for each country differs significantly. Unsurprisingly, country destinations tend to have a larger percentage of travellers with their language preference set to be a native language spoken in that country. For example, Germany (`country_destination = DE`) has the highest proportion of users with a language setting of Deutsche (`language code = DE`). Similar patterns hold for Spain (`country_destination = ES`) and Espanol (`language = ES`). 

Moreover, some countries have large variations of language for users (for example `Other`, since it encapsulates all other countries, has the widest variation of language, as does `France` and `US`), while countries like Australia (`country_destination = AU`) and Portugal (`country_destination = PT`) tend to consist of users from only a few language preferences. 


```{r fig8, eval = TRUE, fig.cap = figure_captions("fig:fig8", "Word cloud of first browser type")}
### First Browser Word Cloud
cloud <-fact.destinations %>% 
  group_by(first_browser) %>% 
  summarize(freq = n())

set.seed(100)
wordcloud(words = cloud$first_browser, freq = cloud$freq, min.freq = 1,scale = c(4,0.5),
          max.words=100, random.order=FALSE, rot.per=0.25, 
          colors=brewer.pal(8, "Dark2"))
```
The most popular browser for user bookings was Google Chrome (33.6%), as evidenced by the word cloud (`r f.ref("fig:fig8")`). Chrome is followed in popularity by Safari (22.2%) and Firefox (17.7%). Almost all users sign up using one of the 5 most common browsers or report `unknown` browser type. The remaining 34 browsers make up less than 2% of all observations. We note that observations which are unknown may require some imputation, or we can simply remove these observations for further analysis. 

## Days from First Active to First Booking
```{r fig9, eval = TRUE, fig.cap = figure_captions("fig:fig9", "Number of days between first activity and first booking by proportion")}
### Distributions: days groups from active to first booking
days_from_active_to_booking_dist2 <- 
  fact.destinations[, .N, by = .(days_from_active_to_booking)
                    ][order(days_from_active_to_booking)
                      ][, ":=" (
                        days_group = ifelse(
                          days_from_active_to_booking == 0,
                          "< 1 day",
                          ifelse(
                            days_from_active_to_booking <= 2,
                            "1 ~ 2 days",
                            ifelse(
                              days_from_active_to_booking <= 7,
                              "3 ~ 7 days",
                              ifelse(
                                days_from_active_to_booking <= 30,
                                "8 ~ 30 days",
                                ifelse(
                                  days_from_active_to_booking <= 90,
                                  "31 ~ 90 days",
                                  ifelse(
                                    days_from_active_to_booking <= 180,
                                    "91 ~ 180 days",
                                    ifelse(
                                      days_from_active_to_booking <= 240,
                                      "181 ~ 240 days",
                                      ifelse(
                                        days_from_active_to_booking <= 300,
                                        "241 ~ 300 days",
                                        "> 300 days"
                                      )
                                    )
                                  )
                                )
                              )
                            )
                          )
                        )
                      )]
days_from_active_to_booking_dist2 <- 
  days_from_active_to_booking_dist2[, .(N = sum(N)), by = .(days_group)
                                    ][, proportion := N / sum(N)
                                    ][, cum_proportion := cumsum(proportion)]
p <- plot_ly() %>% 
  add_trace(
    x = days_from_active_to_booking_dist2$days_group,
    y = days_from_active_to_booking_dist2$proportion,
    type = "bar",
    name = "User %"
  ) %>% 
  add_trace(
    x = days_from_active_to_booking_dist2$days_group,
    y = days_from_active_to_booking_dist2$cum_proportion,
    type = 'scatter',
    mode = 'lines+markers',
    name = "User Cum%"
  ) %>% 
  layout(
    title = "User Proportion in Days from First Active to First Booking",
    xaxis = list(
      title = "Number of Days from First Active to First Booking",
      categoryorder = "array",
      categoryarray = days_from_active_to_booking_dist2$days_group
    ),
    yaxis = list(
      title = "Proportion"
    ),
    legend = list(orientation = 'r')
  )
p
```

The majority of users make their first booking within a week of being first active as evidenced by `r f.ref("fig:fig9")`, suggesting that many users in this dataset first sign up to Airbnb with the intention of making a booking. Moreover, this suggests that for the majority of users who make a first booking, they often sign up to Airbnb once they have decided to travel. 

There are however, users for which there is an extremely long period between first activation to first booking. Due to the time frame of the data, it is reasonable to assume that there are many users currently with the first destination as `NDF` who have made a booking since the end-date of the dataset provided here, and who would therefore also find themselves in the categories with a longer time frame between activation and booking. For these users who record a longer time between activation and booking, it would be reasonable to assume that some initially sign up without intention of making a booking, while others may have intended on booking upon sign up but later chose to book elsewhere. 

# Correlation Analysis

```{r fig10, eval = TRUE, fig.cap = figure_captions("fig:fig10", "Correlation matrix for all continuous variables")}
### Heat Map for All Continuous Variables
dt <- dcast(fact.destinations[, .(id, country_destination)][, key := 1], id ~ country_destination, value.var = "key")
dt[is.na(dt)] <- 0
dt <- merge(
  fact.destinations,
  dt,
  by = "id",
  all.x = TRUE
)

ggcorr(dt,
       nbreaks = 6,
       label = TRUE,
       label_size = 3,
       color = "black",
       hjust = 0.9, 
       size = 3,
       layout.exp = 6)
```

First, we note that the interpretation of these correlations must be done with care, since correlations between some of these variables do not necessarily make sense (for example, the latitude and longitude of destinations, though only weakly correlated here, does not make sense). 

Strong correlations exist between several of the variables. In particular, we note 3 instances where variables are perfectly (or near perfectly) correlated; namely, the longitude of the destination and the distance (in km) to the destination, the `timestamp_first_active` and `first_booking_year`, and finally, `days_from_account_to_booking` and `days_from_active_to_booking`. 

Unfortunately, the majority of strong correlations exist between variables in the countries dataset (ie. the first six variables, from top to bottom) . Since these variables are descriptors of the response variable in question, it is not surprising that there are many high correlations, since the observations from these variables all relate to the same country. This however may present difficulties when training classification models since these variables cannot be used to predict the country destination. 





# Appendix 
We include here several plots of variables whose interpretations may be of interest. A common interpretation across all charts is that when plotted against country, the proportion of each variable category does not appear to be significantly different. As such, we include and discuss these plots here, noting however that the lack of variation in these variables across country may indicate difficulty in using these variables in building our classification model. 

## Signup Method
```{r fig11, eval = TRUE, fig.cap = figure_captions("fig:fig11", "Signup Method Across Country Destinations")}
### 5.4
fact.destinations %>% 
  ggplot(. ,aes(
    reorder(
      country_destination,
      signup_method,
      function(x) - length(x)
    ), 
    fill = signup_method)
  ) +
  geom_bar(position = "fill") + 
  theme_bw() + 
  labs(title = "Signup Method Proportion Across Country Destinations", x = "Country", y = "Proportion") +
  theme(plot.title = element_text(hjust = 0.5))
```
The plot above (`r f.ref("fig:fig11")`) shows a breakdown of the number of the number of users who sign up using 'basic' methods, facebook and google. Clearly most people sign up using the basic method (approximately 73.1%), with only 26.7% of users signing up using facebook, and 0.1% using google to sign up.  

## Affiliate Channel
```{r fig12, eval = TRUE, fig.cap = figure_captions("fig:fig12", "Affiliate Channel Proportion Across Country Destinations")}
### 8.2
fact.destinations %>% 
  ggplot(., aes(
    reorder(
      country_destination, 
      affiliate_channel, 
      function(x) -length(x)
    ), 
    fill = affiliate_channel)
  ) +
  geom_bar(position = "fill") + 
  theme_bw() + 
  labs(title = "Affiliate Channel Proportion Across Country Destinations", x = "Country", y = "Proportion")+
  theme(plot.title = element_text(hjust = 0.5))
```
`r f.ref("fig:fig12")` shows the breakdown of affiliate channel proportion across country destination. Similarly to other plots in this appendix, the proportion across country does not appear to change significantly. The majority of users apply directly through Airbnb. 

## Affiliate Provider
```{r fig13, eval = TRUE, fig.cap = figure_captions("fig:fig13", "Affiliate Provider Across Country")}
### 9
fact.destinations %>% 
  ggplot(., aes(
    reorder(
      country_destination, 
      affiliate_provider, 
      function(x) -length(x)
    ), 
    fill = affiliate_provider)
  ) +
  geom_bar(position = "fill") + 
  theme_bw() + 
  labs(title = "Affiliate Provider Proportion Across Country Destinations", x = "Country", y = "Proportion") + 
  theme(plot.title = element_text(hjust = 0.5))
```
`r f.ref("fig:fig13")` shows the breakdown of affiliate provider proportion across country destination. Similarly to other plots in this appendix, the proportion across country does not appear to change significantly. The majority of users apply directly through Airbnb.

## First Affiliate Tracked
```{r fig14, eval = TRUE, fig.cap = figure_captions("fig:fig14", "First Affiliate Tracked Across Country Destinations")}
### 10.2
fact.destinations %>% 
  ggplot(., aes(
    reorder(
      country_destination,
      first_affiliate_tracked,
      function(x) -length(x)
    ), 
    fill = first_affiliate_tracked)
  ) +
  geom_bar(position = "fill") + 
  theme_bw() + 
  labs(title = "First Affiliate Tracked Across Country Destinations", x = "Country", y = "Proportion") +
  theme(plot.title = element_text(hjust = 0.5))
```

Approximately 90% of the users who made a booking used the website. This is considerably larger than the next largest category, iOS. Due to limited documentation of this variable, we might guess that this refers to the iOS app. Similarly, we can guess that Android refers to users who use the Android app to sign up (approximately 1.4%) and finally, Moweb might refer to users who use a mobile browser to sign up. 

## Signup App
```{r fig15, eval = TRUE, fig.cap = figure_captions("fig:fig15", "Signup App Proportion Across Country Destination")}
### 11.3
fact.destinations %>% 
  ggplot(., aes(
    country_destination, 
    fill = signup_app)
  ) +
  geom_bar(position = "fill") + 
  theme_bw() + 
  labs(title = "Signup App Proportion Across Country Destinations", x = "Country", y = "Proportion") +
  theme(plot.title = element_text(hjust = 0.5))
```
The distribution of signup apps across countries does not appear to differ significantly. The majority of users sign up via the method `Web`. 

## Signup Flow
```{r fig17, eval = TRUE, fig.cap = figure_captions("fig:fig17", "First Affiliate Tracked Across Country Destinations")}
### 11.5
fact.destinations %>% 
  ggplot(., aes(
    country_destination, 
    fill = as.factor(signup_flow)
    )
  ) +
  geom_bar(position = "fill") + 
  theme_bw() + 
  labs(title = "Signup Flow Proportion Across Country Destinations", x = "Country", y = "Proportion") +
  theme(plot.title = element_text(hjust = 0.5))
```
The majority of users sign up using the signup flow `0`. 

## First Device Type
```{r fig16, eval = TRUE, fig.cap = figure_captions("fig:fig16", "Proportion of first device type by country")}
### 12.2
fact.destinations %>% 
  mutate(
    first_device_type_1 = recode(
      first_device_type, 
      "Android Phone" = "Phone", 
      "iPhone" = "Phone",
      "Android Tablet" = "Tablet",
      "iPad" = "Tablet",
      "Windows Desktop" = "Desktop", 
      "Mac Desktop" = "Desktop")
    ) %>% 
  filter(first_device_type_1 == "Phone" | first_device_type_1 == "Tablet"| first_device_type_1 == "Desktop" ) %>% 
  ggplot(., aes(
    reorder(
      country_destination,
      first_device_type_1, 
      function(x) -length(x)
    ), 
    fill = first_device_type_1)
  )+
  geom_bar(position = "fill") + 
  theme_bw() +
  labs(title = "First Device Type: Phone or tablet or desktop") +
  theme(plot.title = element_text(hjust = 0.5))
```

The largest group here was users who use Mac Desktops to sign up. This is followed by Windows Desktop and then iPhone. It appears that the majority of users have initially signed up on an Apple device. 



```{r}

#### Clean the columns got by joining to other csv files ----
suppressWarnings({
  fact.destinations[, ":=" (
    age_bucket = NULL,
    population_in_thousands = NULL,
    lat_destination = NULL,
    lng_destination = NULL,
    distance_km = NULL,
    destination_km2 = NULL,
    destination_language = NULL,
    language_levenshtein_distance = NULL
  )]
})

#### Features Enginnering ----
model_file <- copy(fact.destinations)[, ":=" (
  id = NULL,
  date_account_created = NULL,
  timestamp_first_active = NULL,
  date_first_booking = NULL,
  date_first_active = NULL,
  date_first_booking_end_week = NULL,
  first_active_year_month = NULL,
  first_account_year_month = NULL,
  first_booking_year_month = NULL,
  first_booking_year = NULL
)]

model_file <- model_file[, ":=" (
  gender = as.integer(as.factor(gender)),
  age = as.numeric(age),
  signup_method = as.integer(as.factor(signup_method)),
  signup_flow = as.numeric(signup_flow),
  language = as.integer(as.factor(language)),
  affiliate_channel = as.integer(as.factor(affiliate_channel)),
  affiliate_provider = as.integer(as.factor(affiliate_provider)),
  first_affiliate_tracked = as.integer(as.factor(first_affiliate_tracked)),
  signup_app = as.integer(as.factor(signup_app)),
  first_device_type = as.integer(as.factor(first_device_type)),
  first_browser = as.integer(as.factor(first_browser)),
  country_destination = as.factor(country_destination),
  days_from_active_to_account = as.numeric(days_from_active_to_account),
  days_from_account_to_booking = as.numeric(days_from_account_to_booking),
  days_from_active_to_booking = as.numeric(days_from_active_to_booking)
)]




#### NAs ----
# Check NAs
row.has.na <- apply(model_file, 1, function(x){any(is.na(x))})
sum(row.has.na)

# Remove NAs
model_file <- model_file[complete.cases(model_file),]
which(is.na(model_file))
```


```{r}
library(dplyr)
library(gbm) # boosting
library(UBL) # up and down sampling
library(knitr) # to run the kable
library(xgboost)
library(caret)
```


```{r gmb}

data<- subset(model_file, select = -dataset_type)

set.seed(123)
inTrain <- createDataPartition(data$country_destination, p = .7)[[1]]
train <- data[ inTrain,]
test  <- data[-inTrain,]


# boosting model

## preliminary training

gbm.model <- gbm(country_destination~., data=train, n.trees=500,
                 shrinkage = 0.02,interaction.depth = 3,cv.folds=5,keep.data = FALSE,
                 n.minobsinnode = 40)


# Summary of the model results, with the importance plot of predictors.
summary(gbm.model, las = 2)


# Check the best iteration number.
best.iter <- gbm.perf(gbm.model, method = "cv")
# the optimal ntrees is 405.



# confusion matrix
preds <- predict(gbm.model, newdata = test , n.trees=best.iter, type="response")
preds.max<- colnames(preds)[apply(preds,1,which.max)]

print(mean(preds.max == test$country_destination))

# output


kable(table(test$country_destination,preds.max),format = "markdown")


```
```{r}
model_file <- read.csv("input\\imputed_model_file_Testing.csv", header = T, sep = ",")

row.has.na <- apply(model_file, 1, function(x){any(is.na(x))})

sum(row.has.na)

head(model_file)

dim(model_file)



set.seed(123)
inTrain <- createDataPartition(model_file$country_destination, p = 0.75)[[1]]

fact.destinationsTrain <- model_file[ inTrain, ]
fact.destinationsTest  <- model_file[-inTrain, ]

knn.model <- train(country_destination ~ . ,
                   data = fact.destinationsTrain,
                   method = "knn",  
                   trControl = trainControl(method = "repeatedcv", 
                                            repeats = 5))

knn.train.pred <- predict(knn.model, newdata = fact.destinationsTrain)
knn.train.CM <- confusionMatrix(knn.train.pred, fact.destinationsTrain$country_destination)
knn.train.overall.accuracy <- knn.train.CM$overall['Accuracy']
print(paste0("Training Accuracy: ",knn.train.overall.accuracy))

knn.test.pred <- predict(knn.model, newdata = fact.destinationsTest)
knn.test.CM <- confusionMatrix(knn.test.pred, fact.destinationsTest$country_destination)
knn.test.overall.accuracy <- knn.test.CM$overall['Accuracy']
print(paste0("Test Accuracy: ",knn.test.overall.accuracy))

dim(fact.destinationsTrain)


```

